---
title: "Survey_analysis"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

# Hypothesis 1

## Read data

```{r 1, include=TRUE}

library(readxl)

survey <- read_excel("Survey_Analysis.xlsx")


```

## Removing wrong data

```{r 2, include=TRUE}

survey$code1=ifelse(survey$In10years_youprefer_CW_than_TW=="Strongly agree"|survey$In10years_youprefer_CW_than_TW=="Agree", 2,ifelse(survey$In10years_youprefer_CW_than_TW=="Strongly disagree"|survey$In10years_youprefer_CW_than_TW=="Disagree", 1,0))

survey$code2=ifelse(survey$In10years_youprefer_TW_than_CW=="Strongly agree"|survey$In10years_youprefer_TW_than_CW=="Agree", 2,ifelse(survey$In10years_youprefer_TW_than_CW=="Strongly disagree"|survey$In10years_youprefer_TW_than_CW=="Disagree", 1,0))

sum= 0
v=c()
j=1
for( i in 1: nrow(survey)){  
 if( survey$code1[i]==survey$code2[i]) 
  if( survey$code1[i] !=0){
    sum= sum +1
  v[j]=i
  j=j+1}}

sum

survey=survey[-v,]

```

## Renaming data

```{r 3, include=TRUE}

survey$Gender <- ifelse(survey$Gender == "A man", "Man", "Woman")

```

## Changing data to factors

```{r 4, include=TRUE}

survey$Gender = factor(survey$Gender)

survey$Annual_salary[ survey$Annual_salary == "I prefer not to answer"] = NA

survey$Annual_salary = factor(survey$Annual_salary, c("I don't have a salary","Less than 50K", "Between 50K and 100K", "Between 100K and 150K", "More than 150K"))

survey$Interest_for_TW = factor(survey$Interest_for_TW, c(1,2,3,4,5,6,7,8,9,10))

survey$Age_group = cut(survey$Age, breaks = c(18, 24, 40, 56, Inf), include.lowest = TRUE, right = FALSE, labels = c("Z Generation","Y Generation","X Generation", "Baby-Boomers") )

```

## Creating score

```{r 5, include=TRUE}

survey$Hybridewatches_goodforyou = factor(survey$Hybridewatches_goodforyou, c("Strongly agree", "Agree", "Neutral", "Disagree", "Strongly disagree"))


survey$TW_helpsyou_disconnect = factor(survey$TW_helpsyou_disconnect, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))


survey$Youcouldlivewith_both = factor(survey$Youcouldlivewith_both, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))

survey$CW_willreplace_TW = factor(survey$CW_willreplace_TW, c("Strongly agree", "Agree", "Neutral", "Disagree", "Strongly disagree"))


survey$CW_and_TW_differentuses_cantbecompared = factor(survey$CW_and_TW_differentuses_cantbecompared, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))


survey$IF_brandslaunch_TW_youseethebranddifferenlty = factor(survey$IF_brandslaunch_TW_youseethebranddifferenlty, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))


survey$Notorietywill_decrease_movingawayfromtradition = factor(survey$Notorietywill_decrease_movingawayfromtradition, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))


survey$Notorietywillincrease_becausecapacityofinnovastion = factor(survey$Notorietywillincrease_becausecapacityofinnovastion, c("Strongly agree", "Agree", "Neutral", "Disagree", "Strongly disagree"))


survey$hybride_isnice_compromise = factor(survey$hybride_isnice_compromise, c("Strongly agree", "Agree", "Neutral", "Disagree", "Strongly disagree"))

```

## Calculating Alpha Cronbach

```{r 6, include=TRUE}

library(ltm)

cronbach.alpha(survey[,c(19,24,25,26,27,28,29,30)])

colnames(survey[,c(19,24,25,26,27,28,29,30)])

```

## Creating score

```{r 7, include=TRUE}

set2 = as.data.frame( lapply(survey[,c(19,24,25,26,27,28,29,30)], as.numeric) )

survey$score_H1 = apply(set2, 1, sum)

summary(survey$score_H1)

tapply(survey$score_H1, survey$Gender, mean)

t.test( survey$score_H1, mu=24, alternative = "greater")

```

## Summarising data

```{r 8, include=TRUE}

library(xtable)

summary(survey$score_H1)

```

## Visualization 1

```{r 9, include=TRUE}

library(ggplot2)

ggplot(data = survey, mapping = aes(x=ID, y=score_H1)) + geom_point()+labs(title="Scatter plot of score by respondent", x="Respondent", y="Score")

```

## Visualization 2

```{r 10, include=TRUE}

ggplot(data= survey, aes(x = score_H1)) + geom_histogram( aes(y = stat(width*density)*100 ), color="White"  )+scale_x_continuous("Score", labels = as.character(8:40), breaks = 8:40)+labs(title="Distribution of score in percentage", y="Percentage")

```

## Visualization 3

```{r 11, include=TRUE}

ggplot(data = survey, mapping = aes(x=Interest_for_TW, y=score_H1, group = 1)) + geom_point()+stat_summary(fun =  "mean",  geom = "line")+labs(title="Score of respondents by level of interest", y="Score", x="Are you interested in traditional Swiss watches?")

```

## Visualization 4

```{r 12, include=TRUE}

ggplot(data = survey, mapping = aes(x=Annual_salary, y=score_H1)) + geom_boxplot(width = 0.5) +
  geom_dotplot(binaxis = "y", stackdir = "center", binwidth = 1, fill = "lightgray", dotsize = 0.6)+
  labs(x="What is your annual salary?", y="Score")+theme(axis.text.x = element_text(angle = 30))

```

## Calculating Anova 1

```{r 13, include=TRUE}

one.way <- aov( score_H1 ~ Annual_salary, data = survey)

summary(one.way)

```

## Visualization 5

```{r 14, include=TRUE}

ggplot(data = survey, mapping = aes(x=Age_group, y=score_H1)) + geom_boxplot(width = 0.5) +
  geom_dotplot(binaxis = "y", stackdir = "center", binwidth = 1, fill = "lightgray", dotsize = 0.6)+
  labs(x="Generation", y="Score")

```

## Calculating Anova 2

```{r 15, include=TRUE}

one.way <- aov( score_H1 ~ Age_group, data = survey)

summary(one.way)

```

## Calculating differences

```{r 16, include=TRUE}

TukeyHSD(one.way)

```

## Visualization 6

```{r 17, include=TRUE}

plot(TukeyHSD(one.way))

```

## Calculating the mean

```{r 18, include=TRUE}

tapply(survey$score_H1, survey$Age_group, mean)

```

# Hypothesis 2

## Creating score

```{r 19, include=TRUE}

survey$Happy_toreceive_CW = factor(survey$Happy_toreceive_CW, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))


survey$Happy_toreceive_TW = factor(survey$Happy_toreceive_TW, c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree"))

```

## Calculating correlation

```{r 20, include=TRUE}

set3 = as.data.frame( lapply(survey[,c(17,18)], as.numeric) )

cor.test(set3$Happy_toreceive_CW, set3$Happy_toreceive_TW, method="spearman")

```

## Creating table

```{r 21, include=TRUE}

table(survey$Happy_toreceive_CW, survey$Happy_toreceive_TW)

```

## Visualization 7

```{r 22, include=TRUE}

barplot(table(survey$Happy_toreceive_CW, survey$Happy_toreceive_TW),     
        col = 1:5,
        legend.text = TRUE, 
        beside = T,
        args.legend = list(x = "topleft", title = "You would be happy to receive a connected watch"), ylab = "Number of responses", xlab="You would be happy to receive a traditional Swiss watch
")

```

## Visualization 8

```{r 23, include=TRUE}

barplot(table(survey$Happy_toreceive_TW, survey$Happy_toreceive_CW),     
        col = 1:5,
        legend.text = TRUE, 
        beside = T,
        args.legend = list(x = "topleft", title="You would be happy to receive a traditional Swiss watch", cex=0.75
                          ), ylab = "Number of responses", xlab="You would be happy to receive a connected watch")

```

## Comparing with generations

```{r 24, include=TRUE}

mysum <- function(x){
  sum( x=="Strongly agree" | x=="Agree")
}

tapply(survey$Happy_toreceive_CW, survey$Age_group, mysum)

tapply(survey$Happy_toreceive_TW, survey$Age_group, mysum)

```

## Comparing with generations

```{r 25, include=TRUE}

mysum <- function(x){
  sum( x=="Strongly agree" | x=="Agree")
}

a = tapply(survey$Happy_toreceive_CW, survey$Age_group, mysum) / table(survey$Age_group)*100

a

```

# Comparing with generations

```{r 26, include=TRUE}


b = tapply(survey$Happy_toreceive_TW, survey$Age_group, mysum) / table(survey$Age_group)*100

b

```

## Visualization 9

```{r 27, include=TRUE}

z= data.frame( Generation = levels(survey$Age_group), cbind(a,b))

colnames(z)<- c("Generation", "Connected watch", "Traditional Swiss watch")

library(reshape2)

dd = melt(z, variable.name = "Type", value.name = "Percentage")

ggplot(data=dd) + 
  geom_point(aes( x= Generation , y = Percentage))  + 
  geom_line(  aes( x= Generation , y = Percentage, group=Type, color=Type))+ylim(0,100)

```

## Creating score

```{r 28, include=TRUE}

mysum <- function(x){
  sum( x=="Strongly agree" | x=="Agree")
}

tapply(survey$In10years_youprefer_CW_than_TW, survey$Age_group, mysum)

tapply(survey$In10years_youprefer_TW_than_CW, survey$Age_group, mysum)

```

# Storing in c

```{r 29, include=TRUE}

c = tapply(survey$In10years_youprefer_CW_than_TW, survey$Age_group, mysum) / table(survey$Age_group)*100

c

```

# Storing in d

```{r 30, include=TRUE}

d = tapply(survey$In10years_youprefer_TW_than_CW, survey$Age_group, mysum) / table(survey$Age_group)*100

d

```

## Visualization 10

```{r 31, include=TRUE}

z= data.frame( Generation = levels(survey$Age_group), cbind(c,d))

colnames(z)<- c("Generation", "Connected watch", "Traditional Swiss watch")

library(reshape2)

dd = melt(z, variable.name = "Type", value.name = "Percentage")

ggplot(data=dd) + 
  geom_point(aes( x= Generation , y = Percentage))  + 
  geom_line(  aes( x= Generation , y = Percentage, group=Type, color=Type))+ylim(0,100)

```

# Visualization 11

```{r 32, include=TRUE}

ggplot(data=dd) + 
  geom_col(  aes( x= Generation , y = Percentage, group=Type, fill=Type), position = "dodge")+ylim(0,100)

```

# Visualization 12

```{r 33, include=TRUE}

# Evolution of the percentage of respondant that see themself with \na connected watch rather than a traditional Swiss watch on their wrist

z1= data.frame( Generation = levels(survey$Age_group), cbind(a,c))

colnames(z1)<- c("Generation", "2021", "2031")

dd = melt(z1, variable.name = "Year", value.name = "Percentage")

p1 <- ggplot(data=dd) + 
  geom_col(  aes( x= Generation , y = Percentage, group=Year, fill=Year), position = "dodge")+ylim(0,100)

p1

```

# Visualization 13

```{r 34, include=TRUE}

# Evolution of the percentage of respondant that see them self with \na traditional Swiss watch rather than a connected watch on their wrist

z2= data.frame( Generation = levels(survey$Age_group), cbind(b,d))

colnames(z2)<- c("Generation", "2021", "2031")

dd = melt(z2, variable.name = "Year", value.name = "Percentage")

p2 <- ggplot(data=dd) + 
  geom_col(  aes( x= Generation , y = Percentage, group=Year, fill=Year), position = "dodge")+ylim(0,100)+labs(title="", y="")

p2

```

## Visualization 14

```{r 35, include=TRUE}

library(cowplot)

legend <- get_legend(
  p1 + 
    guides(color = guide_legend(nrow = 1)) +
    theme(legend.position = "bottom")
)


plot_row <- plot_grid( p1+ theme(legend.position="none") , 
                       p1+ theme(legend.position="none") + ylab(NULL),
                       labels= c( "Connected watch", "Traditional Swiss watch" ))

title <- ggdraw() + draw_label("Evolution of preferences in 2021 and 2031", fontface='bold')


plot_grid(title, plot_row, ncol=1,legend,  rel_heights  = c(0.1, 1))

```
